\LARGE \bf Expectation-Maximization based defense mechanism for distributed Model Predictive Control

### 2022-05-16 article/article.tex
correct captions and vectors

\begin{algorithm2e}[h]
  \DontPrintSemicolon%
  $p:=0$\;
  Coordinator initializes $\vec{\theta}\p$ \;
  \Repeat{$\|\vec{\theta}^{(p)} -\vec{\theta}^{(p-1)}\|\leq\epsilon$}{
  Subsystems solve~\eqref{eq:DOP_local}, and send $\optlambdai (\thetai\p)$\;
  Coordinator updates allocations~\eqref{eq:thetaNegot}\;
  $p:=p+1$
}
 \caption{Quantity decomposition-based \acrshort{dmpc}.}\label{alg:quantityAlg}
\end{algorithm2e}

@@

We can get an explicit solution for the dual variables $\vec{\lambda}_{i}[k]$, which are \acrfull{pwa} functions w.r.t. $\vec{\theta}_{i}[k]$:
% \begin{equation}
%   \resizebox{.88\columnwidth}{!}{$
%     \begin{aligned}
%       \label{eq:lambdafuntheta}
%       \lambdaik=
%       \begin{cases}
%         -P_{i}^{1}\thetaik-\vec{s}_{i}^{1}[k]&\text{if}\ G^{1}[k]\thetaik \preceq b^{1}[k] \\
%         \qquad\quad \vdots&\qquad\quad \vdots\\
%         -P_{i}^{N}\thetaik-\vec{s}_{i}^{N}[k]&\text{if}\ G^{N}[k]\thetaik \preceq b^{N}[k] \\
%       \end{cases}
%     \end{aligned}
%     $}
% \end{equation}
\begin{equation}
\resizebox{.88\columnwidth}{!}{$
  \begin{aligned}\label{eq:lambdafuntheta}
    \lambdaik=
    % \begin{cases}
      -P_{i}^{n}\thetaik-\vec{s}_{i}^{n}[k]\text{, if}\ G^{n}[k]\thetaik \preceq b^{n}[k],
    % \end{cases}
  \end{aligned}
  $}
\end{equation}
with $n\in\{1\until N\}$.

The halfspaces defined by the pairs $(G^{n}[k],b^{n}[k])$ represent the combinations of active constraints~\eqref{eq:constraints} for a given time $k$, which vary w.r.t. $\vec{v}_{i}[k]$.

@@

In Fig.~\ref{fig:response3Scenarios}, first, we compare the air temperature in room~I
with its reference (${w_{I}=\input{reference}^{\circ}}$C), and then the
decision variable ${E_{I}(k)}$ with the threshold $\epsilon_{P}$.
Observe that the reference $w_{I}$ is not reached in the nominal behavior (in magenta),
due to power constraints by which the systems are influenced.
As expected, the decision variable lies under the threshold ${\epsilon_{P}=10^{-4}}$ with values of order ${E_{I}^{N}(k)\approx10^{-10}}$.
\begin{figure}[h]
  \centering
 \includegraphics[width=.90\columnwidth,trim=0 .3cm 0 .2cm,clip]{airtemp_roomI/__ErrorWX_command_normErrH.pdf}
  \caption{Air temperature in room I and the decision variable $E_{I}[k]$ for three scenarios: nominal (N), selfish behavior (S),
and selfish behavior with correction.}\label{fig:response3Scenarios}
\end{figure}

>>>>

\begin{algorithm2e}[h]
  \DontPrintSemicolon%
  $p:=0$\;
  Coordinator initializes $\vec{\theta}\p$ \;
  \Repeat{$\|\vec{\theta}^{(p)} -\vec{\theta}^{(p-1)}\|\leq\epsilon$}{
  Subsystems solve~\eqref{eq:DOP_local}, and send $\optlambdai (\thetai\p)$\;
  Coordinator updates allocations~\eqref{eq:thetaNegot}\;
  $p:=p+1$
}
 \caption{Quantity decomposition negotiation.}\label{alg:quantityAlg}
\end{algorithm2e}

@@

We can get an explicit solution for the dual variables $\vec{\lambda}_{i}[k]$, which are \acrfull{pwa} functions w.r.t. $\vec{\theta}_{i}[k]$:
% \begin{equation}
%   \resizebox{.88\columnwidth}{!}{$
%     \begin{aligned}
%       \label{eq:lambdafuntheta}
%       \lambdaik=
%       \begin{cases}
%         -P_{i}^{1}\thetaik-\vec{s}_{i}^{1}[k]&\text{if}\ G^{1}[k]\thetaik \preceq b^{1}[k] \\
%         \qquad\quad \vdots&\qquad\quad \vdots\\
%         -P_{i}^{N}\thetaik-\vec{s}_{i}^{N}[k]&\text{if}\ G^{N}[k]\thetaik \preceq b^{N}[k] \\
%       \end{cases}
%     \end{aligned}
%     $}
% \end{equation}
\begin{equation}
\resizebox{.88\columnwidth}{!}{$
  \begin{aligned}\label{eq:lambdafuntheta}
    \lambdaik=
    % \begin{cases}
      -P_{i}^{n}\thetaik-\vec{s}_{i}^{n}[k]\text{, if}\ G^{n}[k]\thetaik \preceq \vec{b}^{n}[k],
    % \end{cases}
  \end{aligned}
  $}
\end{equation}
with $n\in\{1\until N\}$.

The halfspaces defined by the pairs $(G^{n}[k],\vec{b}^{n}[k])$ represent the combinations of active constraints~\eqref{eq:constraints} for a given time $k$, which vary w.r.t. $\vec{v}_{i}[k]$.

@@

In Fig.~\ref{fig:response3Scenarios}, first, we compare the air temperature in room~I
with its reference (${w_{I}=\input{reference}^{\circ}}$C), and then the
decision variable ${E_{I}(k)}$ with the threshold $\epsilon_{P}$.
Observe that the reference $w_{I}$ is not reached in the nominal behavior (in magenta),
due to power constraints by which the systems are influenced.
As expected, the decision variable lies under the threshold ${\epsilon_{P}=10^{-4}}$ with values of order ${E_{I}^{N}(k)\approx10^{-10}}$.
\begin{figure}[h]
  \centering
 \includegraphics[width=.90\columnwidth,trim=0 .3cm 0 .2cm,clip]{airtemp_roomI/__ErrorWX_command_normErrH.pdf}
  \caption{Air temperature in room I and the decision variable $E_{I}[k]$ for three scenarios: nominal (N), selfish behavior (S),
and selfish behavior with correction (C).}\label{fig:response3Scenarios}
\end{figure}
